---
title: "PCA with machine learning"
author: "Sergazy"
date: "7/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


PCA with R.

when do you want to use PCA?
variables should be independent...
and PCA should be less interpretable.. 


PCA is not only dimension reduction.. 




Feature reduction and  feature extraction

```{r}
dataset=read.csv('Wine.csv')
```


We need extra packages
```{r}
#install.packages('caTools')
library(caTools)
```
Splitting the data into the Training and test
```{r}
set.seed(123)
split= sample.split(dataset$Customer_Segment, SplitRatio = 0.8)
training_set=subset(dataset,split==TRUE)
test_set=subset(dataset,split==FALSE)
```
Feature scaling
```{r}
training_set[-14]=scale(training_set[-14])
test_set[-14]=scale(test_set[-14])
```


We also need extra packages

```{r}
#install.packages('caret')
library(lattice)
library(ggplot2)
library(caret)
```


```{r}
pca=preProcess(x=training_set[-14], method='pca',pcaComp = 2)
training_set=predict(pca,training_set)
training_set=training_set[c(2,3,1)]
test_set=predict(pca,test_set)
test_set=test_set[c(2,3,1)]
```


```{r}
#install.packages('e1071')
library(e1071)
classifier= svm(formula=Customer_Segment~.,data=training_set,type='C-classification', kernel='linear')

```
predict the result
```{r}
y_pred= predict(classifier, newdata = test_set[-3])
```
Making confusion matrix to see how we are doing.

```{r}
cm=table(test_set[,3],y_pred)
cm
```

